Small Language Modelling to Generate Playlists from Song Sequences

### 2023-12-12 docs/FinalReport.tex
Super Duper Final Report
No Longer Draft.... it's Done!

The code we used to acquire and process the dataset, train and evaluate our models is available at \url{https://github.iu.edu/rjdharmc/dlProject}. Note that access to this codebase will require an active account on the IU Enterprise Github instance.

>>>>

The code we used to acquire and process the dataset, train and evaluate our models is available at \url{https://github.iu.edu/rjdharmc/dlProject}.\footnote{Note that access to this codebase will require an active account on the IU Enterprise Github instance.}
